Paper 1 Analysis

### 2015-11-14 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Changed appearance of OMGraph.

  ggplot(aes(x = xlabels, weight = lambda)) + 
  facet_grid(Nest ~ Country) +
  geom_bar(width = 0.5) +
  xlab("") +
  ylab(expression(lambda)) +
  xy_theme() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

>>>>

  ggplot(aes(x = xlabels, weight = lambda)) + 
    facet_grid(Nest ~ Country) +
    geom_bar(fill = "white", colour = "black", width = 0.2) +
    geom_hline(yintercept = 0, colour="gray50", size=0.1) +
    xlab("") +
    ylab(expression(lambda)) +
    xy_theme() + 
    theme(
      axis.text.x = element_text(angle = 90, hjust = 1),
      axis.ticks.x = element_blank()
    )
